---
title: "Lab 03 - Nobel laureates"
author: "Rachel Good"
date: "January 22, 2022"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

There are 935 observations and 26 variables in the nobel laureates dataset.

```{r variable-details}
spec(nobel)
count(nobel)
nrow(nobel)
ncol(nobel)
```

### Exercise 2

```{r new-data-frame}
nobel_living <- nobel %>%
  filter(gender != "org",
         !is.na(country),
         is.na(died_date))

nrow(nobel_living)
```

### Exercise 3

Excluding the category of economics, a large portion of nobel laureates originate outside of the United States, supporting the Buzzfeed article headline about the importance of immigration to American Science. 

```{r mutated-country}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```

```{r filter-subject}
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```

```{r exercise3}
nobel_living_science %>% 
  ggplot(aes(x = country_us)) +
  geom_bar() +
  facet_wrap(~category) +
  coord_flip() +
  labs(title = "Nobel Laureates by Category", subtitle = "A look at country origin",
       x = "Country of Origin", y = "Number of Laureates")
```

### Exercise 4

```{r born-country}
nobel_living <- nobel_living %>% 
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
)
```
...

### Exercise 5
```{r exercise 5}
nobel_living %>% 
  ggplot(aes(x = born_country_us)) +
  geom_bar() +
  facet_wrap(~category) +
  coord_flip() +
  labs(title = "Nobel Laureates by Category", subtitle = "A look at country origin",
       x = "Country of Origin", y = "Number of Laureates")
```
...

### Exercise 6

...
